%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{coverletter} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
%\usepackage{fontspec} %Required for changing main fonts
%\setmainfont{Times New Roman}

\name{Di (Patrick) Lu} % Your name

\address{1119 Maiden Lane Ct Apt 105, Ann Arbor, MI \\ qfdlu@umich.edu \\ (734) 239-0334} % Your phone number and email
\renewcommand{\baselinestretch}{1.3}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{}
\ \newline
\ \newline
Sept. 4, 2017\\
Morgan Stanley\\
1585 Broadway, Manhattan, New York City\\ 
New York 10036, United States\\
\ \newline
Dear hiring manager, \\
\\
I am applying for the Morgan Stanley Equity Research Summer Junior Associate Program. As a first-year master’s student in the University of Michigan’s Quantitative Finance and Risk Management program with experience in equity strategies and research skills, I am interested in this opportunity to gain more experience in market reseach and industry insights. The following skills and experiences will make me an asset to your team:
\begin{rSubsection}{}{}{}{}
\item {\bf \em Ability to conduct in-depth research:} While working with the Strategy Research team of China Securities, I prepared weekly market tracking report including all market indices from Asian, European and U.S. stock market. Based on that, I backtested common strategies with SAS to track their recent market performance. This hands-on experience helped me establish the ability to conduct in-depth research and honed my research skills with quantitative tools.
\item {\bf \em Exposure to technology industry:} During my internship at China international Capital Corporation, I worked in the Special Situation Group to conduct venture lending on NEEQ market. During due dilligence, I interviewed with several CEO and managers of technology startups to prepare investement report on their business startegy, industry landscape and outlook. Through detailed work, I gained knowledge of business models in industries like health care, media, education and online retailor companies. My interests and experiences in industry research make me confident to pursue further practice in this field.
\item {\bf \em Experience with cultivating trading strategy:} My work experience at Huisheng-Guanghua Research Fund gave me the opportunity to translate cutting-edge academic findings into practice. One of my major contributions was testing the effectiveness of the Beneish M-score as a trading signal in Chinese market. I ran the strategy on the Ricequant platform to find that it was not effective as a single indicator but could become effective combined with other items. I would use this experience to assist in creating new strategy as part of the equity research team.

\end{rSubsection}
I hope to bring these skills and experiences to work with your equity research team. I look forward to talking with you about the internship and its expected role in contributing to Morgan Stanley's leading and innovative business. Please feel free to contact me by phone or email.\\

Sincerely,\\
Patrick Lu
\end{rSection}



%----------------------------------------------------------------------------------------

\end{document}
